\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-03 main.tex
abstract

The inference of corresponding Thomas models is provided using Answer Set Programming,
which allows notably an efficient enumeration of (possibly numerous) compatible parametrizations.

>>>>

The inference of corresponding Thomas models is \modLP{implemented} using Answer Set Programming,
which allows an efficient enumeration of (possibly numerous) compatible parametrizations.
